\chameleon{}: Untangling Type Errors Through Interactive Visualization and Exploration

### 2022-12-05 sections/walkthrough.tex
Fix latex errors
Recent changes
John's comments

@@

\begin{figure}[h]
        \centering
        \Description{Maxine using basic mode}
        \includegraphics[width=\linewidth]{images/basic-mode-1.pdf}
        \caption{
            Maxine's code to calculate the sum of a list of integers;
            \chameleon{} reports an error on the expression \texttt{xs}.
            }
            \label{fig:basic-mode-1}
\end{figure}

\begin{figure}[h]
        \centering
        \Description{A screenshot of using basic mode}
        \includegraphics[width=\linewidth]{images/basic-mode-2.pdf}
        \caption{
       Hovering on possible type 1 will limit the highlights 
       in the editor to only the ones (in orange) that support \texttt{x::[a]}.
        }
        \label{fig:basic-mode-2}
\end{figure}

\begin{figure}
        \centering
        \Description{A screenshot of using basic mode}
        \includegraphics[width=\linewidth]{images/basic-mode-3.pdf}
        \caption{
            Hovering on possible type 2 (Fig. \ref{fig:basic-mode-2}-3) will limit the highlights 
            in the editor to only the ones (in blue) that support \texttt{x::Int}.
        }
        \label{fig:basic-mode-3}
\end{figure}

@@

Maxine writes additional code to add only the even numbers in a list of integers.
In this implementation, Maxine reuses the \texttt{sum} function she wrote
earlier. After saving the file, \chameleon{} shows that there is a type error in the
expression \texttt{sum} (Fig. \ref{fig:balance-mode-1}). However, this is not 
helpful because Maxine knows that the implementation of  \texttt{sum} is correct 
because it was verified in the previous task. Switching to
balanced mode, Maxine noticed that \chameleon{} shows two cards: \texttt{sum}
and \texttt{evens}.

\begin{figure}
        \centering
        \Description{A screenshot of using balanced mode}
        \includegraphics[width=\linewidth]images/{balanced-mode-1.pdf}
        \caption{
            Maxine's code to calculate only the sum 
            of even numbers. \chameleon{} reports 
            an error with two candidate expressions.
        }
        \label{fig:balance-mode-1}
\end{figure}

\begin{figure}
   \centering
        \Description{A screenshot of using balanced mode}
        \includegraphics[width=\linewidth]{images/balanced-mode-2.pdf}
        \caption{
            Clicking on the \texttt{evens} card (5) results in the changes in the
            conflicting types panel to show the possible types for \texttt{evens},
            and the changes highlights color to reflect the assumption that the
            definition of \texttt{evens} is the cause of the error.  
        }
        \label{fig:balance-mode-2}
\end{figure}

Maxine therefore clicks on the \texttt{evens} card and \chameleon{} shows two
possible types for the expression \texttt{[Int]} and \texttt{[Int] -> [Int]}
(Fig. \ref{fig:balance-mode-2}). Knowing the expression \texttt{evens} holds
a temporary list of even integers (hence it is of \texttt{[Int]} types), Maxine
knows the Possible type 2 is unintended, and blue in-text highlights must
contain the cause. It does not take long until Maxine realizes that the list 
\texttt{evens} is not supplied to the \texttt{filter} function.

@@

\begin{figure}
        \centering
        \includegraphics[width=\linewidth]{images/advanced-mode-1.pdf}
        \Description{A screenshot of using advanced mode}
        \caption{
            Maxine's code to calculate only the sum 
            of even numbers in advanced mode. 
            The current step is step 5, \chameleon{} 
            explains that the two appearances of expression 
            \texttt{evens} should have the same type.
        }
        \label{fig:advanced-mode-step5}
\end{figure}

\begin{figure}
        \centering
        \includegraphics[width=\linewidth]{images/advanced-mode-2.pdf}
        \Description{A screenshot of using advanced mode}
        \caption{
            In step 6, \chameleon{} 
            explains that \texttt{evens} is defined as
            the expression \texttt{filter isEven}. The left-hand side
            and right-hand side should have the same type.
        }
        \label{fig:advanced-mode-step6}
\end{figure}

\begin{figure}
        \centering
        \includegraphics[width=\linewidth]{images/advanced-mode-3.pdf}
        \Description{A screenshot of using advanced mode}
        \caption{
            In step 7, \chameleon{} 
            explains that \texttt{filter} is applied to 
            the function \texttt{isEven}. Assisting by 
            the type of \texttt{filter} in the 
            Relevant Type Information panel on the bottom
            right, Maxine can find the type error that 
            \texttt{filter} expects two arguments but receives one.
        }
        \label{fig:advanced-mode-step7}
\end{figure}

>>>>

\todo{A bit of redundant/repeated here c.f. prev section - if this is Usage example, again use motivating example in it?}

@@

\begin{figure}[h]
        \centering
        \includegraphics[width=\linewidth]{images/basic-mode-1.pdf}
        \caption{
            Maxine's code to calculate the sum of a list of integers;
            \chameleon{} reports an error on the expression \texttt{xs}.
            }
            \label{fig:basic-mode-1}
\end{figure}

\begin{figure}[h]
        \centering
        \includegraphics[width=\linewidth]{images/basic-mode-2.pdf}
        \caption{
       Hovering on possible type 1 will limit the highlights 
       in the editor to only the ones (in orange) that support \texttt{x::[a]}.
        }
        \label{fig:basic-mode-2}
\end{figure}

\begin{figure}
        \centering
        \includegraphics[width=\linewidth]{images/basic-mode-3.pdf}
        \caption{
            Hovering on possible type 2 (Fig. \ref{fig:basic-mode-2}-3) will limit the highlights 
            in the editor to only the ones (in blue) that support \texttt{x::Int}.
        }
        \label{fig:basic-mode-3}
\end{figure}

@@

Maxine writes additional code to add only the even numbers in a list of integers.
In this implementation, Maxine reuses the \texttt{sum} function she wrote
earlier. After saving the file, \chameleon{} shows that there is a type error in the
expression \texttt{sum} (Fig. \ref{fig:balance-mode-1}). However, this is not   \todo{Add annotation to figure like prev ones i.e. (1) so can refer to in text without reader searching for it?}
helpful because Maxine knows that the implementation of  \texttt{sum} is correct 
because it was verified in the previous task. Switching to
balanced mode, Maxine noticed that \chameleon{} shows two cards: \texttt{sum}
and \texttt{evens}.

\begin{figure}
        \centering
        \includegraphics[width=\linewidth]{images/balanced-mode-1.pdf}
        \caption{
            Maxine's code to calculate only the sum 
            of even numbers. \chameleon{} reports 
            an error with two candidate expressions.
        }
        \label{fig:balance-mode-1}
\end{figure}

\begin{figure}
   \centering
        \includegraphics[width=\linewidth]{images/balanced-mode-2.pdf}
        \caption{
            Clicking on the \texttt{evens} card (5) results in the changes in the
            conflicting types panel to show the possible types for \texttt{evens},
            and the changes highlights color to reflect the assumption that the
            definition of \texttt{evens} is the cause of the error.  
        }
        \label{fig:balance-mode-2}
\end{figure}

Maxine therefore clicks on the \texttt{evens} card and \chameleon{} shows two
possible types for the expression \texttt{[Int]} and \texttt{[Int] -> [Int]}
(Fig. \ref{fig:balance-mode-2}). Knowing the expression \texttt{evens} holds
a temporary list of even integers (hence it is of \texttt{[Int]} types), Maxine
knows the Possible type 2 is unintended, and blue in-text highlights must
contain the cause. It does not take long until Maxine realizes that the list 
\texttt{l} is not supplied to the \texttt{filter} function.

@@

\begin{figure}
        \centering
        \includegraphics[width=\linewidth]{images/advanced-mode-1.pdf}
        \caption{
            Maxine's code to calculate only the sum 
            of even numbers in advanced mode. 
            The current step is step 5, \chameleon{} 
            explains that the two appearances of expression 
            \texttt{evens} should have the same type.
        }
        \label{fig:advanced-mode-step5}
\end{figure}

\begin{figure}
        \centering
        \includegraphics[width=\linewidth]{images/advanced-mode-2.pdf}
        \caption{
            In step 6, \chameleon{} 
            explains that \texttt{evens} is defined as
            the expression \texttt{filter isEven}. The left-hand side
            and right-hand side should have the same type.
        }
        \label{fig:advanced-mode-step6}
\end{figure}

\begin{figure}
        \centering
        \includegraphics[width=\linewidth]{images/advanced-mode-3.pdf}
        \caption{
            In step 7, \chameleon{} 
            explains that \texttt{filter} is applied to 
            the function \texttt{isEven}. Assisting by 
            the type of \texttt{filter} in the 
            Relevant Type Information panel on the bottom
            right, Maxine can find the type error that 
            \texttt{filter} expects two arguments but receives one.
        }
        \label{fig:advanced-mode-step7}
\end{figure}
